Psychological Needs During Intergroup Contact

### 2021-12-23 manuscript.tex
Updates from Overleaf
updated

% add packages
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome5}
\usepackage[normalem]{ulem}
% \usepackage{longtable}
\usepackage{amsmath}
\usepackage{ntheorem}
\usepackage{afterpage}
\usepackage{float}
\usepackage{array}
\usepackage{censor}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{pdfpages}
\usepackage{enumitem}

@@

% Relevance v.02: Conflict is a problem, positive contact as solution, but little research on when daily contact is perceived positive
Conflict between social groups and their individual members remains a prevalent feature of the modern human condition. Experiences of prejudices, discrimination, and animosities with other groups continue to plague the everyday lives of many people around the world. One of the main ameliorations proposed by social psychologists has been the intergroup contact hypothesis. In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}. And even though over the past 70 years, a plethoray of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}, relatively little research has thus far explained when and why people's everyday inter-group interactions are perceived as positive.

>>>>

% add packages
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome5}
\usepackage[normalem]{ulem}
% \usepackage{longtable}
\usepackage{amsmath}
\usepackage{ntheorem}
\usepackage{afterpage}
\usepackage{float}
\usepackage{array}
\usepackage{censor}
\usepackage{pdflscape}
\usepackage{lscape}
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{tabu}

@@

% Relevance v.02: Conflict is a problem, positive contact as solution, but little research on when daily contact is perceived positive
Conflict between social groups and their individual members remains a prevalent feature of the modern human condition. Experiences of prejudices, discrimination, and animosities with other groups continue to plague the everyday lives of many people around the world. One of the main ameliorations proposed by social psychologists has been the intergroup contact hypothesis. In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}. And even though over the past 70 years, a plethora of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}, relatively little research has thus far explained when and why people's everyday inter-group interactions are perceived as positive.
